Modular Deep Encoder-Decoders

### 2016-04-28 paper/draft.tex
fixed to use bibtex

Although we could have used any kind of mapping, we chose to use deep
learning algorithms, as they easily learn hierarchical representations
and have been known to highly outperform other statistical techniques on
natural language tasks. Learning embeddings has been previously done by
\href{References}{{[}1{]}}, although our proposed contribution is
slightly different. \href{References}{{[}1{]}} used deep autoencoders to
obtain a better initialization of the parameters of their model. Our
approach instead is much closer in spirit to the work of Sutskever
\href{References}{{[}3{]}} and Vinyals \href{References}{{[}4{]}}. They
both use encoders on a sequence of data to generate a
\emph{thought-vector} which will then be decoded in the desired terget
sequence. In some sense, our proposal adds the transfer learning
component to their contribution. This approach is also similar to the
work of Karpathy \& al \href{References}{{[}5{]}} where they mapped
images to their captions with embeddings.

@@

%\subsubsection{Baseline System}
We construct two baseline systems, one to classify the journals based on the
content of the articles and the second on their authors. Identical architectures are used for both the baseline
systems. The baseline system is a recurrent neural network with one hidden Long
Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of
both the embedding layer and the LSTM was fixed to 128. The output layer is a
softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \href{References}{{[}6{]}}

@@

\section{References}\label{References}

Part of the relevant literature review. More literature was involved for
the deep learning part.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Supervised Representation Learning: Transfer Learning with Deep
  Autoencoders, Zhuang \& al,
  http://ijcai.org/Proceedings/15/Papers/578.pdf
\item
  Transfer Learning via Dimensionality Reduction, Pan \& al,

  https://www.cse.ust.hk/\textasciitilde{}jamesk/papers/aaai08.pdf
\item
  Sequence to Sequence Learning with Neural Networks, Sutskever \& al,

  http://arxiv.org/abs/1409.3215
\item
  Grammar as a Foreign Language, Vinyals \& al,
  http://arxiv.org/abs/1412.7449
\item
  Deep Fragment Embeddings for Bidirectional Image Sentence Mapping,
  Karpathy \& al, https://cs.stanford.edu/people/karpathy/nips2014.pdf

\item Adaptive Subgradient Methods for Online Learning and Stochastic Optimization, Ducih \& al, http://www.jmlr.org/papers/volume12/duchi11a/duchi11a.pdf
\end{enumerate}

>>>>

Although we could have used any kind of mapping, we chose to use deep
learning algorithms, as they easily learn hierarchical representations
and have been known to highly outperform other statistical techniques on
natural language tasks. Learning embeddings has been previously done by
\cite{zhuang2015supervised}, although our proposed contribution is
slightly different. \cite{zhuang2015supervised} used deep autoencoders to
obtain a better initialization of the parameters of their model. Our
approach instead is much closer in spirit to the work of Sutskever
\cite{sutskever2014sequence} and Vinyals \cite{vinyals2015grammar}. They
both use encoders on a sequence of data to generate a
\emph{thought-vector} which will then be decoded in the desired terget
sequence. In some sense, our proposal adds the transfer learning
component to their contribution. This approach is also similar to the
work of Karpathy \& al \cite{karpathy2014deep} where they mapped
images to their captions with embeddings.

@@

%\subsubsection{Baseline System}
We construct two baseline systems, one to classify the journals based on the
content of the articles and the second on their authors. Identical architectures are used for both the baseline
systems. The baseline system is a recurrent neural network with one hidden Long
Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of
both the embedding layer and the LSTM was fixed to 128. The output layer is a
softmax layer with 14 outputs, one per class. The model minimize a cross-entropy loss using adaptive gradient descent. \cite{duchi2011adaptive}

@@

\bibliography{reference} 
\bibliographystyle{ieeetr}
